Energy and the CES production function

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change faceting of SSE, lambda graph.

ggplot() +
  geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
  geom_vline(aes(xintercept = sse), 
             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
             colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = lambda), 
             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
             colour="gray50", size=0.1) +
  scale_size_manual(values=c(2,4)) +
  scale_shape_manual(values=c(1,0,3,4)) + 
  facet_grid(Country ~ flavor) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
  xlab("SSE") + 
  ylab(expression(lambda)) +
  xy_theme() +
  theme(legend.title=element_blank())
@

%
Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
show factor shares ($\alpha$ values) for CES models for
Portugal and the UK, respectively.
See Table~\ref{tab:CES_abg_equations} for details on the calculation
of factor shares from fitted values of $\delta_1$ and $\delta$.
%
<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- 
    AllCoeffs %>% 
    filter(Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3) %>%
    mutate(nest =   # Change nest to a nicer-looking nest string
             plyr::mapvalues(nest, 
                             from=c("kl", "kle", "lek", "ekl"), 
                             to=c("kl", "(kl)e", "(le)k", "(ek)l")),
           label = # Add a label column
              paste(CSP, flavor, energy, nest, sep=", "),
           label =  # Add row numbers to the label column
              paste(paste0(1:length(label), ". "), label)
    )
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  ### tidyr::spread and tidyr::gather are preferred in most cases now
#   bar_chart_data <- melt(bar_chart_data, 
#                          measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
#                          value.name = "value", 
#                          variable.name = "variable")
  bar_chart_data <-
    bar_chart_data %>% gather( key=variable, value=value, alpha_1 : alpha_3 )

>>>>

ggplot() +
  geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
  geom_vline(aes(xintercept = sse), 
             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
             colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = lambda), 
             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
             colour="gray50", size=0.1) +
  scale_size_manual(values=c(2,4)) +
  scale_shape_manual(values=c(1,0,3,4)) + 
  facet_grid(flavor ~ Country) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
  xlab("SSE") + 
  ylab(expression(lambda)) +
  xy_theme() +
  theme(legend.title=element_blank())
@
%
Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
show factor shares ($\alpha$ values) for CES models for
Portugal and the UK, respectively.
See Table~\ref{tab:CES_abg_equations} for details on the calculation
of factor shares from fitted values of $\delta_1$ and $\delta$.
%
<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- 
    AllCoeffs %>% 
    filter(Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3) %>%
    mutate(nest =   # Change nest to a nicer-looking nest string
             plyr::mapvalues(nest, 
                             from=c("kl", "kle", "lek", "ekl"), 
                             to=c("kl", "(kl)e", "(le)k", "(ek)l")),
           label = # Add a label column
              paste(CSP, flavor, energy, nest, sep=", "),
           label =  # Add row numbers to the label column
              paste(paste0(1:length(label), ". "), label)
    )
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  ### tidyr::spread and tidyr::gather are preferred in most cases now
#   bar_chart_data <- melt(bar_chart_data, 
#                          measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
#                          value.name = "value", 
#                          variable.name = "variable")
  bar_chart_data <-
    bar_chart_data %>% gather( key=variable, value=value, alpha_1 : alpha_3 )
